---
title: "ASP_model_analysis_bic"
author: "Cher"
date: "3/24/2021"
output: html_document
---

This script is an extension of ASP_model_analysis_bic.R by analyzing the difference between AC-AI, PC-PI
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gtools)
library(ggpubr)
library(rstatix)
library(ggpubr)
rm(list = ls())
subj1 <- read_csv("../subj_data/ASP1/ASP1_subj_wide90.csv") 
subj2 <- read_csv("../subj_data/ASP3/ASP3_subj_wide142.csv")

model1 = read_csv('./MODEL1/MODEL1_wide.csv') %>% rename(AC.m=DOC,AI.m=DOI,PC.m=POC, PI.m=POI, AC.sd=DOC_sd,AI.sd=DOI_sd,PC.sd=POC_sd, PI.sd=POI_sd)
model2 = read_csv('./MODEL2/MODEL2_wide.csv') %>% rename(AC.m=DOC,AI.m=DOI,PC.m=POC, PI.m=POI, AC.sd=DOC_sd,AI.sd=DOI_sd,PC.sd=POC_sd, PI.sd=POI_sd)
model3 = read_csv('./MODEL3/MODEL3_wide.csv') %>% rename(AC.m=DOC,AI.m=DOI,PC.m=POC, PI.m=POI, AC.sd=DOC_sd,AI.sd=DOI_sd,PC.sd=POC_sd, PI.sd=POI_sd)

#load("./ASP_model_data.RData")
```


# SETUP
func for 4 point estimation
```{r}
# single sub to model
subj2sim <- function(subj, model.r, k, n) {
  sim0 = subj %>%
    merge.data.frame(model.r) %>%
    mutate(AC.z=(AC-AC.m)/pmax(AC.sd, 1e-10),
           AI.z=(AI-AI.m)/pmax(AI.sd, 1e-10),
           PC.z=(PC-PC.m)/pmax(PC.sd, 1e-10),
           PI.z=(PI-PI.m)/pmax(PI.sd, 1e-10),
           AC.prob_z=dnorm(AC.z, 0, 1), 
           AI.prob_z=dnorm(AI.z, 0, 1),
           PC.prob_z=dnorm(PC.z, 0, 1),
           PI.prob_z=dnorm(PI.z, 0, 1),
           logL=log(AC.prob_z)+log(AI.prob_z)+log(PC.prob_z)+log(PI.prob_z),
           bic=convert_bic(k, n, logL))
  return(sim0)
}
```

func for 7 point estimation
```{r}
subj2sim <- function(subj, model.r, k, n) {
  sim0 = subj %>%
    merge.data.frame(model.r) %>%
    mutate(AC.z=(AC-AC.m)/pmax(AC.sd, 1e-10),
           AI.z=(AI-AI.m)/pmax(AI.sd, 1e-10),
           PC.z=(PC-PC.m)/pmax(PC.sd, 1e-10),
           PI.z=(PI-PI.m)/pmax(PI.sd, 1e-10),
           diff.ACAI.z=(diff.ACAI-diff.mACAI)/max(diff.mACAI.sd, 1e-10),
           diff.PCPI.z=(diff.PCPI-diff.mPCPI)/max(diff.mPCPI.sd, 1e-10),
           diff.CI.z=(diff.CI-diff.mCI)/max(diff.mCI.sd, 1e-10),
           
           AC.prob_z=dnorm(AC.z, 0, 1), 
           AI.prob_z=dnorm(AI.z, 0, 1),
           PC.prob_z=dnorm(PC.z, 0, 1),
           PI.prob_z=dnorm(PI.z, 0, 1),
           diff.ACAI.prob_z=dnorm(diff.ACAI.z, 0, 1), 
           diff.PCPI.prob_z=dnorm(diff.PCPI.z, 0, 1), 
           diff.CI.prob_z=dnorm(diff.CI.z, 0, 1), 
           
           logL=log(AC.prob_z)+log(AI.prob_z)+log(PC.prob_z)+log(PI.prob_z)
           +log(diff.CI.prob_z)+log(diff.ACAI.prob_z)+log(diff.PCPI.prob_z),
           bic=convert_bic(k, n, logL))
  return(sim0)
}
```

func for calculating bic
```{r}
# define bic 
convert_bic <- function(k, n, logL) {
  return(k * log(n) - 2 * logL)
}

subj2model <- function(subj, model, k, n) {
  datalist = list()
  for (i in 1:nrow(model)) {
    model.r=model[i,]
    dat = subj2sim(subj, model.r, k, n)
    datalist[[i]] <- dat
  }
  result = data.frame(do.call(rbind, datalist))
  return(result)
}
```
# SUBJ1
calculate diff.mACAI, diff.mPCPI, and sd of difference

The Central Limit Theorem: 
Let  have a normal distribution with mean , variance , and standard deviation .
Let  have a normal distribution with mean , variance , and standard deviation .
If  X and Y are independent, then X-Y will follow a normal distribution with mean mu1-mu2, variance var1+var2, and standard deviation sqrt(sd1^2+sd2^2).

The varaicen fo a difference is the sum of the varience varc-i = var(c) + var(i)
```{r}
# calculate se from proportion

# # calculate combined variance for AC AI
# calculate_combined_mean_sd <- function(mean1, mean2, sd1, sd2, n1, n2) {
#   mean_combined = (n1*mean1 + n2*mean2)/(n1+n2)
#   var_combined = (n1*(sd1^2 + (mean1-mean_combined)^2) + n2*(sd2^2 + (mean2-mean_combined)^2))/(n1+n2)
#   return(sqrt(var_combined))
# }

# source: https://online.stat.psu.edu/stat500/lesson/7/7.3/7.3.1/7.3.1.1
pooled_mean_sd <- function(mean1, mean2, sd1, sd2, n1, n2) {
  sd_pooled = sqrt( ((n1-1)*sd1^2 + (n2-1)*sd2^2) / (n1+n2-2) )
  return(sd_pooled)
}

# source: https://online.stat.psu.edu/stat500/lesson/7/7.1
diff_mean_sd <- function(sd1, sd2) {
  sd_diff = sqrt(sd1^2 + sd2^2)
  return(sd_diff)
}

# source: https://online.stat.psu.edu/stat500/lesson/7/7.2/7.2.1
# prop_sd <- function(p1, n1) {
#   sd1 = p1*(1-p1)/n1
#   return(sd1)
# }
# 
# prop_diff_sd <- function(p1, p2, n1, n2) {
#   sd = p1*(1-p1)/n1 + p2*(1-p2)/n2
#   return (sd)
# }

# calculate diff between AC.m-AI.m and PC.m-PI.m and sd of difference
calculate_diff <- function(model1){
  model1.new = model1 %>% 
  mutate(C.m = (AC.m+PC.m)/2,
         I.m = (AI.m+PI.m)/2,
         C.sd = pooled_mean_sd(AC.m, PC.m, AC.sd, PC.sd, 100, 100),
         I.sd = pooled_mean_sd(AI.m, PI.m, AI.sd, PI.sd, 100, 100),
         
         diff.mACAI = AC.m-AI.m,
         diff.mPCPI = PC.m-PI.m, 
         diff.mCI = C.m - I.m,
         
         diff.mACAI.sd = diff_mean_sd(AC.sd, AI.sd), 
         diff.mPCPI.sd = diff_mean_sd(PC.sd, PI.sd),  
         diff.mCI.sd = diff_mean_sd(C.sd, I.sd), 
         )
  return(model1.new)
}

calculate_prop_diff <- function(model1) {
  model1.new = model1 %>% 
  mutate(C.m = (AC.m+PC.m)/2,
         I.m = (AI.m+PI.m)/2,
         C.sd = prop_sd(C.m, 100),
         I.sd = prop_sd(I.m, 100),
         
         diff.mACAI = AC.m-AI.m,
         diff.mPCPI = PC.m-PI.m, 
         diff.mCI = C.m - I.m,
         
         diff.mACAI.sd = prop_diff_sd(AC.m, AI.m, 50, 50),
         diff.mPCPI.sd = prop_diff_sd(PC.m, PI.m, 50, 50), 
         diff.mCI.sd = prop_diff_sd(C.m, I.m, 100, 100), 
         )
  return(model1.new)
}
```


7 point: calculate diff 
```{r}
# calculate diff.ACAI
subj1 = subj1 %>% mutate(diff.ACAI = AC-AI, diff.PCPI = PC-PI, diff.CI = C-I)
subj2 = subj2 %>% mutate(diff.ACAI = AC-AI, diff.PCPI = PC-PI, diff.CI = C-I)


model1 = calculate_diff(model1)
model2 = calculate_diff(model2)
model3 = calculate_diff(model3)

# calculate diff.ACAI
```

func categorize best fit model
```{r}
# categorize best model
categorize_best_model <- function(subj1model1, subj1model2, subj1model3) {
  subj1models <- subj1model1 %>% 
  group_by(subjID) %>% 
  slice(which.min(bic)) %>% 
  select(subjID:mid, bic, logL, AC.m:PI.m) %>%
  full_join(subj1model2 %>% 
              group_by(subjID) %>% 
              slice(which.min(bic)) %>% 
              select(subjID, mid, bic, logL), 
            by = 'subjID', suffix=c('.m1', '.m2')) %>%
  full_join(subj1model3 %>% 
              group_by(subjID) %>% 
              slice(which.min(bic)) %>% 
              select(subjID, mid, bic, logL) %>%
              setNames(c(names(.)[1], paste0(names(.)[-1],".m3"))) %>% 
              arrange(subjID), by = 'subjID') %>%
  ungroup(subjID)
  
  # categorize
  bestmodels <- subj1models %>%
  rowwise() %>%
  mutate(min_bic = pmin(bic.m1, bic.m2, bic.m3)) %>%
  bind_cols(best_model = colnames(subj1models %>% select(starts_with("bic")))[apply(subj1models %>% 
                                                                                  select(starts_with("bic")),1,which.min)])
  
  return (bestmodels)
}

# calcualte relative loglikelihood
calculate_relativelogL <- function(subj1bestmodels) {
  LL1 <- subj1bestmodels %>% 
  select(logL.m1, logL.m2, logL.m3) %>% 
  colSums(na.rm = TRUE)
  rLL1 <- LL1-min(LL1)
  rLL.dat1 <- data.frame(LL = LL1, rLL = rLL1,
                       dLL.nullm1 = c(LL1[[1]]-LL1[[1]], LL1[[2]]-LL1[[1]], LL1[[3]]-LL1[[1]]),
                       dLL.nullm2 = c(LL1[[1]]-LL1[[2]], LL1[[2]]-LL1[[2]], LL1[[3]]-LL1[[2]]),
                       dLL.nullm3 = c(LL1[[1]]-LL1[[3]], LL1[[2]]-LL1[[3]], LL1[[3]]-LL1[[3]]),
                       model=c("m1", "m2", "m3"))
  return (rLL.dat1)
}


# calculate group bayes factor
calculate_GBF <- function(rLL) {
  rLL %>%
    select(model, starts_with("dLL")) %>%
    mutate_at(vars(matches("dLL")), exp)
}

```


plot func
```{r}
# plot pie
plot_piechart <- function(subj1bestmodels) {
  plot.pie1 <- subj1bestmodels %>%
  group_by(best_model) %>% 
  summarise(n = n()) %>% 
  mutate(freq = (round(n / sum(n), 4)),best_model = factor(gsub("min.", "", best_model))) %>% 
  arrange(desc(best_model)) %>%
  mutate(ypos = cumsum(freq) - 0.5*freq) %>%
  ggplot(aes(x="", y=freq, fill=best_model)) +
  geom_bar(stat="identity", width = 1, color="white") +
  geom_text(aes(y = ypos,label = paste0(freq*100, "%")), color = "white", size=8) +
  coord_polar("y", start = 0) +
  scale_fill_discrete(name = "Best fit model", 
                      labels = c("m1: Declarative Model", 
                                 "m2: Associative Model", 
                                 "m3: Reinforcement Model")) +
  ggtitle('The percentage of subjects best fit by model simulation output') +
  theme_void() 
  return(plot.pie1)
}

# plot hist
plot_bichist <- function(subj1model1, subj1model2, subj1model3) {
  plot.hist1 <- subj1model1 %>% select(bic) %>% mutate(model="m1") %>% 
  bind_rows(subj1model2 %>% select(bic) %>% mutate(model="m2")) %>%
  bind_rows(subj1model3 %>% select(bic) %>% mutate(model="m3")) %>%
  filter(bic<500) %>%
  mutate(model=factor(model)) %>%
  gghistogram(x = "bic", bins = 100, col = "white", fill = "model", alpha = .9)  + 
  scale_fill_discrete(name = "Models", 
                      labels = c("m1: Activation Model", 
                                 "m2: Associative Model", 
                                 "m3: Reinforcement Model")) +
  theme(text = element_text(size = 20))     
  return(plot.hist1)
}

# plot relative log-likelihood
plot_relativelogL <- function(rLL.dat1) {
  plot.llplot1 <- rLL.dat1 %>% ggbarplot(x="model", y="rLL", fill="model",lab.nb.digits = 2, 
          label = rLL.dat1$rLL, lab.pos = "in", lab.size = 8, lab.col = "white") +
    labs(y = "relative log-likelihood") +
  theme(text = element_text(size = 20), legend.position="None")
  return(plot.llplot1)
}

```

# SUBJ1
```{r}
# combine subj + model
subj1model1  = subj2model(subj1, model1, k=3, n=4) #90*150=13,500
subj1model2 = subj2model(subj1, model2, k=5, n=4) #90*1440=129,600
subj1model3 = subj2model(subj1, model3, k=4, n=4) #90*900=81,900

# categorize best
subj1bestmodels = categorize_best_model(subj1model1, subj1model2, subj1model3) %>% 
  filter(bad_subj==F) # remove bad subj
```

```{r}
rLL.dat1 <- calculate_relativelogL(subj1bestmodels)
gbf.dat1 <- calculate_GBF(rLL.dat1)

plot.pie1 <- plot_piechart(subj1bestmodels)
plot.hist1 <- plot_bichist(subj1model1, subj1model2, subj1model3) + ggtitle("Experiment 1 Fit: BIC distribution of three models")
plot.llplot1 <- plot_relativelogL(rLL.dat1) + ggtitle("Experiment 1 Fit: Relative Log-Likelihood")


# combine three plots
plot.exp1 <- ggarrange(plot.hist1, plot.llplot1, ncol = 2, nrow = 1, labels = c("A", "B"), common.legend = T, legend = "bottom") 

plot.exp1
```

test
why relative-ll shows m2 is the best, but pie chart shows m3 is the best
```{r}
rLL.dat1
subj1model1 %>% select(AC, AC.m, AC.sd, AC.z) %>%
  mutate(((AC-AC.m)/max(AC.z, 1e-10))==AC.z, ((AC-AC.m)/AC.z) == AC.z)

subj1model1 %>% select(ends_with(".prob_z"), logL, bic) %>% #colnames()
  mutate(log(AC.prob_z) + log(AI.prob_z) + log(PC.prob_z) + log(PI.prob_z))

# check probz and logL inf - done
subj1model1 %>% select(mid, ends_with(".prob_z"), logL, bic) %>% 
  filter_at(vars(-mid, -logL, -bic), any_vars(. == 0.0)) %>% View()

# check z score calculation
subj1model1 %>% select(ends_with(".prob_z"), logL, bic) %>%
  mutate(v1=log(AC.prob_z) + log(AI.prob_z) + log(PC.prob_z) + log(PI.prob_z), convert_bic(logL=v1,k=3,n=4)) 

# check bic 
temp1 <- subj1model1 %>% select(mid, subjID, logL, bic) %>% filter_all(any_vars(!is.infinite(bic))) %>%
  group_by(subjID) %>%
  slice(which.min(bic)) 
temp2 <- subj1model2 %>% select(mid, subjID, logL, bic) %>% filter_all(any_vars(!is.infinite(bic))) %>%
  group_by(subjID) %>%
  slice(which.min(bic)) 
temp3 <- subj1model3 %>% select(mid, subjID, logL, bic) %>% filter_all(any_vars(!is.infinite(bic))) %>%
  group_by(subjID) %>%
  slice(which.min(bic)) 

full_join(temp2, temp3, by="subjID", suffix=c(".m2", ".m3")) %>% select(subjID, starts_with("bic")) %>%
  mutate(diff.m2m3 = bic.m2-bic.m3) %>%
  #gather("m", "bic", bic.m2:bic.m3) %>%
  #ggbarplot(x="subjID", y="diff.m2m3")
  gghistogram(x="diff.m2m3", binwidth = .1)
rLL.dat1


# check relatitve ll
subj1bestmodels %>% select(ends_with("m1"))
subj1model3

#calculate_relativelogL()
LL1 <- subj1bestmodels %>% select(starts_with("logL")) %>%
  colSums()
rLL1 <- LL1-min(LL1)

subj1bestmodels %>%
  gghistogram(x="best_model", stat="count")
```



# SUBJ2

Comb
```{r}
subj2 <- subj2 %>% rename(subjID=surveyID, AC=DOC,AI=DOI, PC=POC, PI=POI)
# combine subj + model
subj2model1  = subj2model(subj2, model1, k=3, n=4) #141*150=21,150
subj2model2 = subj2model(subj2, model2, k=5, n=4) #141*1440=203,040
subj2model3 = subj2model(subj2, model3, k=4, n=4) #141*900=126,900


# categorize best
subj2bestmodels = categorize_best_model(subj2model1, subj2model2, subj2model3) %>%
  filter(bad_subj == F)
  #anti_join(subj2 %>% filter(bad_subj==TRUE), by="subjID") # remove bad subj


# subj2model1.new  = subj2model(subj2.new, model1, k=3, n=4) #125*150=21,150
# subj2model2.new = subj2model(subj2.new, model2, k=5, n=4) #125*1440=203,040
# subj2model3.new = subj2model(subj2.new, model3, k=4, n=4) #125*900=126,900
# 
# subj2model1.old  = subj2model(subj2.old, model1, k=3, n=4) #141*150=21,150
# subj2model2.old = subj2model(subj2.old, model2, k=5, n=4) #141*1440=203,040
# subj2model3.old = subj2model(subj2.old, model3, k=4, n=4) #141*900=126,900
# 
# subj2bestmodels.new = categorize_best_model(subj2model1.new, subj2model2.new, subj2model3.new)
# subj2bestmodels.old = categorize_best_model(subj2model1.old, subj2model2.old, subj2model3.old)
```



Visualize
```{r}
rLL.dat2 <- calculate_relativelogL(subj2bestmodels) 
gbf.dat2 <- calculate_GBF(rLL.dat2)


plot.pie2 <- plot_piechart(subj2bestmodels)
plot.hist2 <- plot_bichist(subj2model1, subj2model2, subj2model3) + 
  ggtitle("Experiment 2 Fit: BIC distribution of three models") +
  theme(text = element_text(size = 20))     

plot.llplot2 <- plot_relativelogL(rLL.dat2) + 
  ggtitle("Experiment 2 Fit: Relative Log-Likelihood") +
  theme(text = element_text(size = 20))     


# combine three plots
plot.exp2 = ggarrange(plot.hist2, plot.llplot2, ncol = 2, nrow = 1, labels = c("A", "B"), common.legend = T, legend = "bottom")
plot.exp2
```


# TEST
```{r}
subj1model1 %>%  colnames()
subj1model1.temp <- subj1model1 %>% select(AC, AC.m, AC.sd, AC.z)
subj1model1.temp %>% mutate((AC-AC.m)/max(AC.sd, 1e-10))

subj1model1 %>% select(ends_with(".sd")) 
```


# INDIVIDUAL DIFF 
```{r}
# 6 subject plots
subj1bestmodels.temp = subj1bestmodels %>%  
  select(subjID, mid.m1, mid.m2, mid.m3, bic.m1, bic.m2, bic.m3, AC:PI, AC.m.m1:PI.m.m1, 
         AC.m.m2:PI.m.m2, AC.m.m3:PI.m.m3,min_bic, best_model) %>%
  arrange(min_bic) %>%
  group_by(best_model) %>% slice(1:2)

plot.indi1 = subj1bestmodels.temp %>%
  gather('P_type', 'mean_prop', AC:PI.m.m3) %>% 
  mutate(P_type = str_replace(P_type, '.m', ''),
         D_type = case_when(str_detect(P_type, ".m1") ~ "m1", str_detect(P_type, ".m2") ~ "m2", str_detect(P_type, ".m3") ~ "m3", TRUE ~ "subject"),
         P_type = case_when(str_detect(P_type, "AC") ~ "AC", str_detect(P_type, "AI") ~ "AI", str_detect(P_type, "PC") ~ "PC",  str_detect(P_type, "PI") ~ "PI", TRUE ~ "subject"),
         syn_voice = ifelse(P_type=="AC"|P_type=="AI", "Active", "Passive"),
         syn_corr = ifelse(P_type=="AC"|P_type=="PI", "Correct", "Incorrect")) %>% 
  ggplot(aes(x = syn_voice, y = mean_prop, group = interaction(syn_voice, syn_corr), col = syn_corr)) +
  geom_point(aes(shape = D_type), size = 5, position = position_dodge(width=0.75)) +
  scale_shape_manual(name="Model vs. Subject", values=c(0, 1, 2, 8)) +
  ggsci::scale_color_jco(name="Prime Condition: syntactic correctness") +
  geom_text(data=subj1bestmodels.temp, aes(x=1.5, y=1.2, label=paste0("min bic: ", round(min_bic, 2))), 
            inherit.aes=FALSE, parse=FALSE) +
  geom_text(data=subj1bestmodels.temp, aes(x=1.5, y=1.1, label=paste0("best fit model: ", str_replace(best_model, 'bic.', ''))), 
            inherit.aes=FALSE, parse=FALSE) +
  facet_grid(.~subjID) +
  ggtitle("Experiment 1: Individual subject fit by models") + 
  labs(x = "Conditions", y = "Proportion of Actice descriptions") + 
  theme(legend.position = 'bottom')

plot.indi1
```

```{r}
# 6 subject plots
subj2bestmodels.temp = subj2bestmodels.new %>%
  tibble::rowid_to_column("subjID2") %>%
  select(subjID2, mid.m1, mid.m2, mid.m3, bic.m1, bic.m2, bic.m3, min_bic, best_model, AC:PI, AC.m.m1:PI.m.m1, AC.m.m2:PI.m.m2, AC.m.m3:PI.m.m3) %>%
  arrange(min_bic) %>%
  group_by(best_model) %>% slice(1:2)

plot.indi2 = subj2bestmodels.temp %>%
  gather('P_type', 'mean_prop', AC:PI.m.m3) %>% 
  mutate(P_type = str_replace(P_type, '.m', ''),
         D_type = case_when(str_detect(P_type, ".m1") ~ "m1", str_detect(P_type, ".m2") ~ "m2", str_detect(P_type, ".m3") ~ "m3", TRUE ~ "subject"),
         P_type = case_when(str_detect(P_type, "AC") ~ "AC", str_detect(P_type, "AI") ~ "AI", str_detect(P_type, "PC") ~ "PC",  str_detect(P_type, "PI") ~ "PI", TRUE ~ "subject"),
         syn_voice = ifelse(P_type=="AC"|P_type=="AI", "DO", "PD"),
         syn_corr = ifelse(P_type=="AC"|P_type=="PI", "Correct", "Incorrect")) %>% 
  ggplot(aes(x = syn_voice, y = mean_prop, group = interaction(syn_voice, syn_corr), col = syn_corr)) +
  geom_point(aes(shape = D_type), size = 5, position = position_dodge(width=0.75)) +
  facet_grid(.~subjID2) +
  geom_text(data=subj2bestmodels.temp, aes(x=1.5, y=1.2, label=paste0("min bic: ", round(min_bic, 2))), 
            inherit.aes=FALSE, parse=FALSE) +
  geom_text(data=subj2bestmodels.temp, aes(x=1.5, y=1.1, label=paste0("best fit model: ", best_model)), 
            inherit.aes=FALSE, parse=FALSE) +
  ggtitle("Experiment 2: Individual subject fit by models") + 
  labs(x = "Conditions", y = "Proportion of Actice descriptions") + 
  scale_shape_manual(name="Model vs. Subject", values=c(0, 1, 2, 8)) +
  ggsci::scale_color_jco(name="Prime Condition: syntactic correctness") +
  theme(legend.position = 'bottom')


plot.indi1
plot.indis = ggarrange(plot.indi1, plot.indi2,
          labels = c("A", "B"),
          ncol = 1, nrow = 2)
```


# HIST

############################################


```{r}
subj1models.histdat = subj1model1 %>% select(bic) %>% mutate(model="m1") %>% 
  bind_rows(subj1model2 %>% select(bic) %>% mutate(model="m2")) %>%
  bind_rows(subj1model3 %>% select(bic) %>% mutate(model="m3")) %>%
  filter(bic<500) %>%
  mutate(model=factor(model))
  #mutate(model=factor(case_when(model=="m1" ~"Declarative model", model=="m2" ~"Spreading model",model=="m3" ~"Reinnforcement model", TRUE ~ "")))

subj2models.histdat = subj2model1 %>% select(bic) %>% mutate(model="m1") %>% 
  bind_rows(subj2model2 %>% select(bic) %>% mutate(model="m2")) %>%
  bind_rows(subj2model3 %>% select(bic) %>% mutate(model="m3")) %>%
  filter(bic<500) %>%
  mutate(model=factor(model))
  #mutate(model=factor(case_when(model=="m1" ~"Declarative model", model=="m2" ~"Spreading model",model=="m3" ~"Reinnforcement model", TRUE ~ "")))

levels(subj1models.histdat$model) <- c("Declarative model","Associative model", "Reinnforcement model")
levels(subj2models.histdat$model) <- c("Declarative model","Associative model", "Reinnforcement model")


bic.histplot = ggarrange(
  subj1models.histdat %>% gghistogram(x = "bic", bins = 100, col = "model", fill = "model", alpha = .3) +
    ggtitle("Experiment1: BIC histogram of three models "),
  subj2models.histdat %>% gghistogram(x = "bic", bins = 100, col = "model", fill = "model", alpha = .3) +
    ggtitle("Experiment2: BIC histogram of three models "), 
  subj1models.histdat %>% ggdensity(x="bic", col = "model",  fill = "model", alpha = .3) + theme(legend.position = "none"),
  subj2models.histdat %>% ggdensity(x="bic", col = "model", fill = "model", alpha = .3) + theme(legend.position = "none"),
  common.legend = TRUE, legend = "bottom"
)

bic.histplot
```


# Simulation Plot
```{r}
#Simulation plot
plot_simulation <- function(dat.model) {
  plot.model <- dat.model %>% select(mid, AC.m, AI.m, PC.m, PI.m) %>% 
  gather("P_type", "prop_isactive", AC.m:PI.m) %>% 
  mutate(syn_voice = ifelse(P_type=="AC.m"|P_type=="AI.m", "Active", "Passive"),
         syn_corr = ifelse(P_type=="AC.m"|P_type=="PC.m", "Correct", "Incorrect")) %>%
  ggbarplot(x = "syn_corr", y = "prop_isactive", add = "mean_ci",
            fill = "syn_voice", color = "black",size = 1, 
            palette = 'jco', position = position_dodge(0.8))  + 
  ylim(0, 1) + 
  labs(x = "Prime grammaticality", 
       y = "Mean proportion of active descriptions", 
       fill = "Prime syntactic structure")
  return (plot.model)
}

plot.simulation <- ggarrange(plot_simulation(model1) + ggtitle("Averaged simulation results of model 1 (Activation Model)"), 
          plot_simulation(model2) + ggtitle("Averaged simulation results of model 2 (Associative Model)"),
          plot_simulation(model3) + ggtitle("Averaged simulation results of model 3 (Reinforcement Model)"), 
          ncol = 3, nrow=1)
  

plot.simulation
```


